\documentclass[10pt, oneside]{article}   	
\parskip= 5pt
\parindent= 0pt

\usepackage[left=0.8in,top=0.8in,right=0.8in,bottom=1in]{geometry}  
\usepackage{xcolor}           		
\geometry{letterpaper}                   		
		
\usepackage{graphicx}				
\usepackage{textcomp}
\usepackage{sourcecodepro}
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage{currvita}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
% set itemize spacing
\usepackage{enumitem}
\setitemize{itemsep=-1.5pt}

\usepackage{soul}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
%\usepackage[utf8]{inputenc}
%\usepackage{tgpagella}
\usepackage{palatino}
%\usepackage{garamond}
\usepackage{verbatim}

\usepackage[normalem]{ulem}
\usepackage{contour}
\renewcommand{\ULdepth}{1.7pt}
\contourlength{0.8pt}
\contournumber{100}
\usepackage{fontawesome}
%\newcommand*\faMobile{{\FA\symbol{"F10B}}}
\newcommand{\ultight}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}
% C++ logo
\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}


% horizontal line
\newcommand{\hRule}[1]{\textcolor[RGB]{110,110,110}{\rule{#1\linewidth}{0.2pt}}}

\newcommand{\hRuleShort}{\centerline{\textcolor[RGB]{110,110,110}{\rule{0.63\linewidth}{0.2pt}}}}

\renewcommand{\baselinestretch}{1.0} 
% Change the typewriter font
\renewcommand{\ttdefault}{cmvtt}
% \definecolor{linkColor}{RGB}{166,0,0} % RED
\definecolor{linkColor}{RGB}{0,0,166} % BLUE
\begin{document}	

%\begin{cvlist}
\vspace{-10pt}
\centerline{\huge  \textbf{Alexander Wickstrom}}
        \vspace{2mm}
%	 \item\centerline{1440 Veteran Ave, Los Angeles, CA 90024}
\centerline{ \faMobile{} 414-779-7102 \quad \faEnvelope{} awickstrom@ucla.edu 
\quad{\color{linkColor}\ultight{{\href{https://www.linkedin.com/in/alexander-wickstrom-429b8b53/}{Linkedin}}}}\quad{\color{linkColor} \ultight{\href{https://www.researchgate.net/profile/Alexander_Wickstrom}{ResearchGate}}}}

%%%% INTRODUCTION
% Who I am
% What I can bring to the table
% Career aim
%%% INTERESTS
\begin{comment}
{\large  \textbf{Interests}}

     Applying neural engineering to biomedicine. Specifically: \vspace{-2mm}
     \begin{enumerate}
     \setlength{\parskip}{1pt}
        \item Online machine learning for chronic neural recordings
        \item Bidirectional brain-computer interfaces
       \item Cortical prosthetics
     %   \item Non-invasive cognition enhancement    
     \end{enumerate}
\end{comment}
%\vspace{-1pt}
%\hRuleShort{} \vspace{-10pt}

\centerline{1440 Veteran Ave. \quad Los Angeles, CA}
\vspace{-2pt}
\begin{center}
    %{\large  \textbf{Summary}}
An engineer with 5 years experience in Python and MATLAB, specializing in machine learning, data analysis, and signal processing.
Also familiar with {\textsf{R}}, SQL, and C\hspace{-0.5pt}\texttt{+\hspace{-1pt}+}.% \\ A motivated team player adept at executing solo projects. 
\end{center}
% \vspace{-12pt}
%     \hRuleShort{}
     
%\subsection*{}
%\vspace{9mm}
{\Large  \textbf{Education}}  \hrulefill

\textbf{Master of Science:} Bioengineering  (Neuroengineering subfield) \hfill{Sept. 2016 - June 2019}\\
\textit{University of California, Los Angeles} (UCLA) \hfill GPA: 3.7/4.0

        Thesis: {\color{linkColor}{\href{https://escholarship.org/uc/item/0bt7x5mm}{\ultight{Neural Dynamics of Human Seizures}}}}\\
         Thesis Chair: Wentai Liu, Ph.D. \quad Co-Chair: Jonathan Kao, Ph.D. 
         
        
% {University of California, Los Angeles} (UCLA)

\textbf{Bachelor of Science:} Biological Sciences \hfill  Jan. 2012 - Dec. 2015\\
\textit{University of Wisconsin-Milwaukee} (UWM) \hfill GPA: 3.7/4.0

Certificate: Premedical Studies\\

%\begin{cvlist}{Research Interests}%
	%\item I am interested in pursuing a graduate education in biomedical engineering. \newline Specifically, I am interested in an interdisciplinary training program that incorporates both computational modeling and laboratory techniques to develop breakthroughs in clinical and investigative neuromodulation. %neural prosthesis technology. 
%\end{cvlist}

%\renewcommand\ttdefault{sourcecodepro}

{\Large  \textbf{Research}} \hrulefill
    % Kao Lab
    
    \textbf{Graduate Student Researcher}\hfill Feb. 2018 --- June 2019 {\color{linkColor}
    
    \href{https://seas.ucla.edu/~kao/people.html}{\ultight{Neural Computation and Engineering Laboratory}}} \phantom{}-- Signal Processing + Machine Learning (UCLA) \quad \\
     \textit{Principal Investigator: Jonathan Kao, Ph.D.}
    \begin{itemize}[topsep=0.5pt]
        \item Processed a large (2TB+) dataset of broadband electrical signals from intracranial depth electrodes.
        \item Wrote custom software to extract single- and multi-unit spiking activity.
        \item Applied statistical and machine learning techniques to find temporal structure in human neural data. 
        \item  Trained CNNs to predict seizures (with up to 98\% accuracy) using TensorFlow on a remote Linux server. % for seizure prediction
        \item Built \texttt{hoopSort} software, a spike-sorting GUI in MATLAB.
    \end{itemize}
    
    %\newpage    
    
    % Diba Lab
	\textbf{Undergraduate Research Assistant} \hfill May 2015 --- Aug. 2016 {\color{linkColor}
	% http://neuralcircuits.uwm.edu
	
	\href{http://sites.lsa.umich.edu/diba-lab/lab-alumni/}{\ultight{Diba Neural Circuits \& Memory Laboratory}}} -- Computational Neuroscience (UWM)\\
	\textit{Principal Investigator: Kamran Diba, Ph.D.}
	% reword
	\begin{itemize}[topsep=0.5pt]
	    \item Built computational models of spiking recurrent neural networks in MATLAB.
	    % \item Explored dynamic properties of recurrent spiking networks with conduction delays and spike-timing dependent plasticity. 
	    \item Developed a new model of forward and reverse replay in neural populations trained on temporal \newline sequences.
%	    \item Modeled memory encoding and retrieval.   	
	\end{itemize}
     
    % Swain Lab
	\textbf{Undergraduate Research Assistant}  \hfill  Aug. 2013 --- Jan. 2016 {\color{linkColor}
	
	\href{https://sites.google.com/site/swainlabuwm/home}{\ultight{Swain Behavioral Neuroscience Laboratory}}} -- Behavioral Neuroscience (UWM) \\
	\textit{Principal Investigator: Rodney Swain, Ph.D.}
	\begin{itemize}[topsep=0.5pt]
	    \item 	Innovated critical solutions for drug preparation.
        %\item  Assisted with behavioral testing; 
        \item Performed drug injections, craniotomies, and durotomies on adult rats, along with %Vascular imaging via SD-OCT.
		 whole-animal perfusion and brain extraction.
		 \item 		 Used Leica\textregistered  \phantom{} Cryostat to prepare brain tissue for microscopy.  % on Leica CryoStat.
		 \item 		 Compiled statistical analyses in MATLAB.
	\end{itemize}
%	\vspace{-5pt}

{\Large{\textbf{Work Experience}}}  \hrulefill

    \textbf{Dev Engineer Jr.} \hfill June 2019 --- Present
    
    {\color{linkColor}
    \href{https://seas.ucla.edu/~kao/}{\ultight{Neural Computation and Engineering Laboratory}}} (UCLA)
    \begin{itemize}[topsep=0.5pt]
        \item  Refining deep learning models for seizure prediction.
        %\item Editing a manuscript for submission.
    \end{itemize}
    \newpage
    % TA for DeepLearning - Kao's class
    \vspace{3pt}
   \textbf{Teaching Assistant} \hfill Jan. --- June 2019
   
 {\color{linkColor}\href{https://seas.ucla.edu/~kao/nndl/index.html}{\ultight{ECE 239AS}}}: Neural Networks \& Deep Learning (UCLA)\\
    \textit{Professor: Jonathan Kao, Ph.D.}
    \begin{itemize}[topsep=0.5pt]
        \item   Recorded video discussion sections and held in-person office hours. 
        \item    Wrote and graded exam questions. Responded to student questions via Piazza web service.
    \end{itemize}
  % TA for MachineLearning BioEng
  \vspace{3pt}
    \textbf{Teaching Assistant}  \hfill Jan. --- June 2018
    
     %\underline{\smash{\href{https://bioe-ml-w18.github.io/bioe-ml-winter2018/}{BIOENGR 188}}}:
    {\color{linkColor}
    \href{https://aarmey.github.io/ml-for-bioe/}{\underline{\smash{BIOENGR C275}}}}:
    % Special Courses in Bioengineering -
     Machine Learning \& Data-driven Modeling in Bioengineering (UCLA)\\
    \textit{Professor: Aaron Meyer, Ph.D.}
    \begin{itemize}[topsep=0.5pt]
        \item  Led discussion sections in a computer lab and held office hours.
        \item Taught examples of machine learning concepts \newline (regression, dim. reduction, clustering, HMMs, SVMs, etc.) using slideshows and Jupyter notebooks.
    \end{itemize}
     
%\vspace{-5pt}


% 	\item \textbf{Volunteer} \hfill February 2011 | August 2014
% 	\item \underline{\smash{Columbia St. Mary\textquotesingle s Hospital}}
% 	\item Three years experience: Intensive Care Unit
% 	\item One year experience: Emergency Department

%\newpage
%
%
%
%
%
%
%
\begin{comment}
\vspace{5mm}
{\large \textbf{Presentations}}%\vspace{-118mm}

\textbf{Wickstrom, A.T.} Spectral domain optical coherence tomography for the assessment of cerebrovascular plasticity.  Poster presented at: Society for Neuroscience, annual meeting. November 15, 2016. San Diego, CA.

 \textbf{Wickstrom, A.T.} Cerebrovascular Plasticity Assessed by Spectral-Domain Optical \newline Coherence Tomography.
	\color{blue}\href {https://sites.google.com/site/atwreferencesapril2015/}{Poster} \color{black}presented at:\hspace{2pt}\color{blue}\href{http://dc.uwm.edu/uwsurca/2015/Poster1/55/}{\textit{14th Annual UW System Symposium}}\newline
	\color{black}\textit{for Undergraduate Research \& Creative Activity}; April 24, 2015. Milwaukee, WI.
\color{blue}

\color{black}
 \textbf{Wickstrom, A.T.} Optogenetic Manipulation of Thalamic Reticular Subnetworks. \newline Oral presentation delivered at:\hspace{2pt}\color{blue}\href{https://sites.google.com/site/uwmnci/}			{\textit{UWM Neuronal Control \& Interference Journal Club}}\color{black}; December 11, 2014. Milwaukee, WI.

 \textbf{Wickstrom, A.T.}, Behnke, V.K., \& Garnett, E.D. Exercise, Learning, and the Expression of HIF-1$\alpha$ in the
	Hippocampus of the Adult Rat. 
	Poster presented at:\hspace{3pt}\textit{13th Annual UW System Symposium for Undergraduate Research \& Creative Activity}; 
	April 11, 2014. Milwaukee, WI.
\end{comment}
%\begin{cvlist}{Conferences Attended}
%	\item Annual Meeting of the Society for Neuroscience.  \hfill{November 12-16, 2016}
%		\item San Diego, CA
%	\item Annual Meeting of the Society for Neuroscience.  \hfill{October 17-21, 2015}
%		\item Chicago, IL
%\end{cvlist}
%\begin{cvlist}{Publications}
%	\item Stevenson, M.E., Wickstrom, A.T., Behnke, V.K., \& Swain, R.A. Vascular plasticity modulates neurogenesis. \textit{In Preparation}, 2016.
%\end{cvlist}
%\vspace{5mm}
%\vspace{-12pt}


{\Large \textbf{Publications}} \hrulefill

\textbf{Wickstrom, A.} \& Kao, J.C. (2020).  Power in spiking band predicts seizure onset. \textit{Manuscript in Progress}

Stevenson, M. E., Kay, J. J., Atry, F., \textbf{Wickstrom, A.}, Krueger, J. R., Pashaie, R. E., \& Swain, R. A. (2019).\\ Wheel Running for 26 Weeks is Associated with Sustained Vascular Plasticity in the Rat Motor Cortex. \\ \textit{Behavioural Brain Research}, 112447.

\begin{comment}
\textbf{Wickstrom, A.}, Lyttle, D. \& Diba, K. (2020). Forward and reverse replay in a recurrent network with STDP. (2020).\\
\end{comment}
% MEMBERSHIPS 
\begin{comment}


{\Large \textbf{Memberships}} \hrulefill % \underline{Neuronal Control \& Interference Journal Club}  (UWM) \hfill{Fall 2014}

 \textbf{Institute of Electrical and Electronics Engineers} \hfill{Jan. 2016 --- Present}\newline
	 \phantom{9mm} Engineering in Medicine and Biology Society 
%	\item \hspace{9mm} Biometrics Council
%	\item \hspace{9mm} Nanotechnology Council

	 \textbf{Society for Neuroscience} \hfill{Oct. 2015 --- Present} \newline
%	 \hspace{-1.5mm}  \textbf{American Chemical Society} \hfill{2015 --- Present}
	 \phantom{9mm} Biochemical Technology Division
	 
	 \textbf{American Medical Student Association}  (UWM chapter) \hfill{Jan. 2012 --- Dec. 2015} \newline
	 \phantom{9mm}Volunteer Coordinator \hfill{Jan. 2013 --- June 2014} \newline
	 \phantom{9mm}Chair of Race, Ethnicity, and Culture in Health \hfill{Jan. --- June 2014}  
\end{comment}
% SFN Oct. 17-21, 2015
%\vspace{5mm}
{\Large \textbf{Certifications}} \hrulefill

    \textbf{Responsible Conduct of Research Involving Humans}:  David Geffen School of Medicine, UCLA
 
% 	\item  \textbf{Standard First Aid}: American Academy of Orthop\ae dic Surgeons/American College of Emergency Physicians
% 	\item  \textbf{Adult, Child, Infant CPR}: AAOS/ACEP
% 	\item  \textbf{Automated External Defibrillator}: AAOS/ACEP

	  \textbf{Basic Life Support for Healthcare Providers}: American Heart Association
	  
	%\item  \textbf{Lab and Chemical Safety Training} (Completed at UWM)
	 %\textbf{Hazardous Waste Handling} (Completed at UWM) 
	 \textbf{Emergency Medical Technician}: Nat. Reg. of Emergency Medical Technicians (Registry \# E3093180)

{\Large \textbf{References}} \hrulefill
\begin{table}[h!]
    \begin{tabular}{ll}
         Wentai Liu, Ph.D. &\faEnvelope{} wentai@ucla.edu \\
Jonathan Kao, Ph.D. &  \faEnvelope{} kao@seas.ucla.edu\\
Kamran Diba, Ph.D. &\faEnvelope{} kdiba@umich.edu \\
Rodney Swain, Ph.D. & \faEnvelope{} rswain@uwm.edu   
    \end{tabular}
\end{table}



% \newpage


\begin{comment}

    \begin{cvlist}{Technical Skills}
    %	\item \textbf{Hardware  \hspace{150pt}     Software}
    %	\item Arduino microcontrollers  \hspace{90pt}     MATLAB  %
    %	\item Soldering,  \hspace{62pt} Python
    %	
    %	\item \hspace{9mm} circuit board etching \hspace{126pt}  CadSoft EAGLE 
    %	\item Stand-alone EEG prototype (in progress) \hspace{19pt} \LaTeX
        \vphantom{a}
        \phantom{a}
        \item 
        \item
        \vspace{-3mm}
            %\caption{My caption}
            %\label{my-label}
            \hspace{-2mm}
            \begin{tabular}{lll} 
                \textbf{Hardware}   & \textbf{Software} &    \\
                Arduino microcontrollers & MATLAB   &    \\
                Soldering                & Python   &    \\
                Circuit Board Etching    & EAGLE    &   
            \end{tabular}
    \end{cvlist}
    
\end{comment}


%\begin{cvlist}{Projects}
%\item tDCS prototype (completed) \hspace{74pt} R


%\begin{cvlist}{References}
%\item
%\end{cvlist}

%\begin{cvlist}{Relevant Coursework}
 %   \item \textbf{UCLA}
 %   \item Signals \& Systems \hfill  2017
 %   \item Signal and Image Processing in Biomedicine  \hfill 2017
 %   \item Nonlinear Dynamical Systems | ODEs \hfill 2017
 %   \item Computational Modeling and Simulation of Biol. Systems  \hfill 2017
 %   \item Machine Learning for Bioinformatics  \hfill 2017
 %   \item  Neural Systems \& Anatomy \hfill 2017
 %   \item Dynamics of Neural Microcircuits \hfill 2017
 %   \item Neuroengineering  \hfill 2016
    % UWM
 %   \item \textbf{UWM}
 %   \item Probability Models \hfill 2016
 %   \item Linear Algebra + Differential Equations \hfill 2015
 %   \item Neuropharmacology \hfill 2015
 %   \item Neuroscience \hfill 2015
 %   \item Physiological Psychology \hfill 2014
 %   \item Neuropsychology \hfill 2013
    
%\end{cvlist}

\end{document}  