\documentclass[10pt, oneside]{article}   	
\parskip= 12pt
\parindent= 0pt

\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}  
\usepackage{xcolor}           		
\geometry{letterpaper}                   		
		
\usepackage{graphicx}				
\usepackage{textcomp}
\usepackage{sourcecodepro}
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage{currvita}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{soul}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
%\usepackage[utf8]{inputenc}
%\usepackage{tgpagella}
\usepackage{palatino}
%\usepackage{garamond}
\usepackage{verbatim}
\usepackage[normalem]{ulem}
\usepackage{contour}
\renewcommand{\ULdepth}{1.7pt}
\contourlength{0.8pt}
\contournumber{100}
\usepackage{fontawesome}
%\newcommand*\faMobile{{\FA\symbol{"F10B}}}
\newcommand{\ultight}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\jobTitle}{Clinical Data Research Analyst }
\newcommand{\company}{UCLA}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%


\newcommand{\hRule}{\textcolor[RGB]{110,110,110}{\rule{\linewidth}{0.2pt}}}

\renewcommand{\baselinestretch}{1.0} 
% Change the typewriter font
\renewcommand{\ttdefault}{cmvtt}
% \definecolor{linkColor}{RGB}{166,0,0} % RED
\definecolor{linkColor}{RGB}{0,0,166} % BLUE



\begin{comment}
ALWAYS include a cover letter!

- TO: (as specific as you can get)

- Quick Review:
  Why should they care? 
    I'm interested in; I'm a fan of; I'd like to apply for . . . 
    
- The Pitch:

    This is what it's all about.
    You're a fan of the comapny.
    Show how you're familiar with the company.
    At least get on the mailing list; subscribing list, etc. 
    Set up: "Here's who I am, here;s what I'm asking for; and this is why"
    Put yourself in PERSPECTIVE: Tell your story here in 1 or 2 or 3 sentences.
    You want the recruiter to be excited for the CV; or motivate them to actually read the CV.
    
- Next Steps: 
\end{comment}


\begin{document}	

%\begin{cvlist}

\centerline{\huge  \textbf{Alexander Wickstrom}}
        \vspace{1mm}
%	 \item\centerline{1440 Veteran Ave, Los Angeles, CA 90024}
\centerline{ \faMobile{} 414-779-7102 \quad \faEnvelope{} awickstrom@ucla.edu }
January 20, 2020


Dear hiring manager:

Thank you for the opportunity to apply for the role of \jobTitle  at \company. Based on the job description and requirements listed, I believe the position would be a great fit for my skillset and interests. I hope you\textquotesingle ll agree.

I am passionate about applying data analysis and machine learning to biomedicine. In my first coding project during my Bachelor of Science, I built computational models of spiking neural circuits in MATLAB to investigate learning and memory phenomena. As part of my Master's thesis, I applied state-of-the-art signal processing and machine learning techniques to identify and visualize structure in a 40kHz time-series dataset recorded from inside the brains of UCLA patients. I also trained deep neural networks in Python (using Keras as a TensorFlow API) to predict seizures from this data.  

Along the way, I have learned to effectively use SciPy, scikit-learn, and other Python packages for signal processing and machine learning. I regularly made use of several powerful MATLAB toolboxes, like Statistics \& Machine Learning and Signal Processing. A combination of coursework and laboratory work have prepared me to skillfully handle a variety of data modalities, including raw images, electrical signals, and text files. I\textquotesingle ve also become proficient on the command line while training models remotely on my lab\textquotesingle s Ubuntu server. I\textquotesingle ve completed training as an Emergency Medical Technician, and earned an A+ in a UCLA course for Responsible Conduct of Research Involving Humans. Finally, I\textquotesingle ve learned to be a proactive team member who can produce results with minimal supervision. 

I am looking to join a motivated team to work on exciting challenges in an environment where I can further develop my skills as a data scientist and engineer. I would love to learn more about your needs for the \jobTitle position, and I would welcome the chance to provide further insight into my experience with machine learning and data analysis. In the meantime, I invite you to review my achievements in the attached CV. 

Thank you for considering my candidacy for this position. I look forward to hearing from you! 

Sincerely,\\
Alex
\end{document}