\documentclass[10pt, oneside]{article}   	
\parskip= 6pt
\parindent= 0pt

\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}  
\usepackage{xcolor}           		
\geometry{letterpaper}                   		
		
\usepackage{graphicx}				
				\usepackage{textcomp}					
\usepackage{ragged2e}
\usepackage{amssymb}
\usepackage{currvita}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}

\usepackage{soul}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%\usepackage{tgpagella}
\usepackage{palatino}
\usepackage{verbatim}

\usepackage[normalem]{ulem}
\usepackage{contour}
\renewcommand{\ULdepth}{1.7pt}
\contourlength{0.7pt}

\newcommand{\ultight}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}
\renewcommand{\baselinestretch}{1.0} 
\begin{document}	

%\begin{cvlist}

\centerline{\Large  \textbf{Alexander Wickstrom}}
        \vspace{1mm}
%	 \item\centerline{1440 Veteran Ave, Los Angeles, CA 90024}
	\centerline{414-779-7102}
  	 \centerline{awickstrom@ucla.edu} 
%\end{cvlist}

%\vspace{-8mm}
\begin{cvlist}{Education}
    \item \textbf{MS, Bioengineering} (Neuroengineering) \hfill{June 2019}
    
    \item {University of California, Los Angeles} (UCLA)
	\item \textbf{BS, Biological Sciences}\hfill  Dec. 2015
	\item \quad Certificate: Premedical Studies
	\item {University of Wisconsin-Milwaukee} (UWM)
\end{cvlist}
\vspace{-10mm}
%
%\begin{cvlist}{Research Interests}%
	%\item I am interested in pursuing a graduate education in biomedical engineering. \newline Specifically, I am interested in an interdisciplinary training program that incorporates both computational modeling and laboratory techniques to develop breakthroughs in clinical and investigative neuromodulation. %neural prosthesis technology. 
%\end{cvlist}
%
%
%
%
%
%
%
\begin{cvlist}{Interests}
     \item Applying neural control engineering to biomedicine. Specifically: 
     \begin{enumerate}
        \item Online machine learning for neural recordings
        \item Bidirectional brain-computer interfaces
        \item Non-invasive cognition enhancement
          \item Cortical prosthetics
     \end{enumerate}
\end{cvlist}
\vspace{-10mm}
%
%
%
%
%
\begin{cvlist}{Research}
    % Kao Lab
    \item \textbf{Graduate Student Researcher}  \hfill Feb. 2018 --- Present \color{blue}
    \item \href{https://seas.ucla.edu/~kao/}{\ultight{Neural Computation and Engineering Laboratory}} \color{black}  - UCLA\\
    Organizing and processing large-scale brain data from intracranial depth electrodes. Extracting single- and multi-unit spiking activity. Using statistical and machine learning techniques to find structure in neural data across time. Training deep learning models for seizure prediction. 
    
    Principal Investigator: Jonathan Kao\\
    Thesis Advisor: Wentai Liu
    
    % Diba Lab
	\item \textbf{Undergraduate Research Assistant} \hfill May 2015 --- Aug. 2016 \color{blue}
	\item \href{http://neuralcircuits.uwm.edu}{\ultight{Diba Neural Circuits \& Memory Laboratory}}  \color{black} - UWM
	% reword
	\item Used MATLAB to build computational models of neural networks. Explored dynamic properties of recurrent spiking networks with conduction delays and spike-timing dependent plasticity. Developed a model of forward and reverse replay in cells trained on a temporal sequence. Modeled memory encoding and retrieval.   	
	
	Principal Investigator: Kamran Diba
    % Swain Lab
	\item \textbf{Undergraduate Research Assistant}  \hfill  Aug. 2013 --- Jan. 2016 \color{blue}
	\item \href{https://sites.google.com/site/swainlabuwm/home}{\ultight{Swain Behavioral Neuroscience Laboratory}} \color{black} - UWM 
	\item Innovated critical solutions for drug preparation.
  		 Assisted with behavioral testing. \\
		 Performed craniotomies, durotomies on adult rats.
	     Vascular imaging via spectral-domain optical coherence
			tomography.
		 Whole-animal perfusion, brain extraction.
		 Prepared tissue sections for microscopy.  % on Leica CryoStat.
		 Trained on ImageJ and SPOT imaging software.
		 
		 Principal Investigator: Rodney Swain
			\newline

% 	\item \textbf{Volunteer} \hfill February 2011 | August 2014
% 	\item \underline{\smash{Columbia St. Mary\textquotesingle s Hospital}}
% 	\item Three years experience: Intensive Care Unit
% 	\item One year experience: Emergency Department
\end{cvlist}
\newpage
%
%
%
%
%
%
%
\begin{cvlist}{Teaching}
    \item \textbf{Teaching Assistant}
    Deep Learning
    Professor: Jonathan Kao
  % TA for MachineLearning BioEng
    \item \textbf{Teaching Assistant}  \hfill Winter 2018
    \item \color{blue} %\underline{\smash{\href{https://bioe-ml-w18.github.io/bioe-ml-winter2018/}{BIOENGR 188}}}:
    \href{https://aarmey.github.io/ml-for-bioe/}{\underline{\smash{BIOENGR 188}}}:
    % Special Courses in Bioengineering -
    \color{black} Machine Learning \& Data-driven Modeling in Bioengineering - UCLA
    
    Professor: Aaron Meyer, Ph.D.
\end{cvlist}
%
%
%
%
%
\vspace{-10mm}
\begin{cvlist}{Presentations}%\vspace{-118mm}
	\item \textbf{Wickstrom, A.T.} Spectral domain optical coherence tomography for the assessment of cerebrovascular plasticity.  Poster presented at: Society for Neuroscience, annual meeting. November 15, 2016. San Diego, CA.
	\item \textbf{Wickstrom, A.T.} Cerebrovascular Plasticity Assessed by Spectral-Domain Optical \newline Coherence Tomography.
		\color{blue}\href {https://sites.google.com/site/atwreferencesapril2015/}{Poster} \color{black}presented at:\hspace{2pt}\color{blue}\href{http://dc.uwm.edu/uwsurca/2015/Poster1/55/}{\textit{14th Annual UW System Symposium}}\newline
		\color{black}\textit{for Undergraduate Research \& Creative Activity}; April 24, 2015. Milwaukee, WI.
	\color{blue}
	
	\color{black}
	\item \textbf{Wickstrom, A.T.} Optogenetic Manipulation of Thalamic Reticular Subnetworks. \newline Oral presentation delivered at:\hspace{2pt}\color{blue}\href{https://sites.google.com/site/uwmnci/}			{\textit{UWM Neuronal Control \& Interference Journal Club}}\color{black}; December 11, 2014. Milwaukee, WI.
	\item \textbf{Wickstrom, A.T.}, Behnke, V.K., \& Garnett, E.D. Exercise, Learning, and the Expression of HIF-1$\alpha$ in the
		Hippocampus of the Adult Rat. 
		Poster presented at:\hspace{3pt}\textit{13th Annual UW System Symposium for Undergraduate Research \& Creative Activity}; 
		April 11, 2014. Milwaukee, WI.
	
\end{cvlist}
\vspace{-3mm}

%\begin{cvlist}{Conferences Attended}
%	\item Annual Meeting of the Society for Neuroscience.  \hfill{November 12-16, 2016}
%		\item San Diego, CA
%	\item Annual Meeting of the Society for Neuroscience.  \hfill{October 17-21, 2015}
%		\item Chicago, IL
%\end{cvlist}

\vspace{-8mm}

%\begin{cvlist}{Publications}
%	\item Stevenson, M.E., Wickstrom, A.T., Behnke, V.K., \& Swain, R.A. Vascular plasticity modulates neurogenesis. \textit{In Preparation}, 2016.
%\end{cvlist}
\vspace{3mm}

\begin{cvlist}{Memberships} % \underline{Neuronal Control \& Interference Journal Club}  (UWM) \hfill{Fall 2014}
\vspace{-2mm}
\item \textbf{Institute of Electrical and Electronics Engineers} \hfill{2016 --- Present}
	\item \hspace{9mm} Engineering in Medicine and Biology Society 
%	\item \hspace{9mm} Biometrics Council
%	\item \hspace{9mm} Nanotechnology Council

	\item \textbf{Society for Neuroscience} \hfill{2015 --- Present}
	\item \hspace{-1.5mm}  \textbf{American Chemical Society} \hfill{2015 --- Present}
	\item \hspace{9mm} Biochemical Technology Division
	\item \textbf{American Medical Student Association}  (UWM) \hfill{Spring 2012 --- 2015} 
	\item \hspace{10mm}Chair of Race, Ethnicity, and Culture in Health \hfill{Spring 2014}  
	\item \hspace{10mm}Volunteer Coordinator \hfill{Spring 2013 --- Spring 2014}
		
	
\end{cvlist}
% SFN Oct. 17-21, 2015
\vspace{-10mm}
\begin{cvlist}{Certifications}
	\vspace{-1mm}
	\item  \textbf{Emergency Medical Technician}: National Registry of Emergency Medical Technicians (Registry \# E3093180)
% 	\item  \textbf{Standard First Aid}: American Academy of Orthop\ae dic Surgeons/American College of Emergency Physicians
% 	\item  \textbf{Adult, Child, Infant CPR}: AAOS/ACEP
% 	\item  \textbf{Automated External Defibrillator}: AAOS/ACEP
	\item  \textbf{Basic Life Support for Healthcare Providers}: American Heart Association
	\item  \textbf{Lab and Chemical Safety Training} (Completed at UWM)
	\item  \textbf{Hazardous Waste Handling Training} (Completed at UWM) 
	\item \textbf{Responsible Conduct of Research Involving Humans} (Completed at UCLA)
\end{cvlist}
% \newpage

\begin{comment}

    \begin{cvlist}{Technical Skills}
    %	\item \textbf{Hardware  \hspace{150pt}     Software}
    %	\item Arduino microcontrollers  \hspace{90pt}     MATLAB  %
    %	\item Soldering,  \hspace{62pt} Python
    %	
    %	\item \hspace{9mm} circuit board etching \hspace{126pt}  CadSoft EAGLE 
    %	\item Stand-alone EEG prototype (in progress) \hspace{19pt} \LaTeX
        \vphantom{a}
        \phantom{a}
        \item 
        \item
        \vspace{-3mm}
            %\caption{My caption}
            %\label{my-label}
            \hspace{-2mm}
            \begin{tabular}{lll} 
                \textbf{Hardware}   & \textbf{Software} &    \\
                Arduino microcontrollers & MATLAB   &    \\
                Soldering                & Python   &    \\
                Circuit Board Etching    & EAGLE    &   
            \end{tabular}
    
    \end{cvlist}

\end{comment}


%\begin{cvlist}{Projects}
%\item tDCS prototype (completed) \hspace{74pt} R


%\begin{cvlist}{References}
%\item
%\end{cvlist}

%\begin{cvlist}{Relevant Coursework}
 %   \item \textbf{UCLA}
 %   \item Signals \& Systems \hfill  2017
 %   \item Signal and Image Processing in Biomedicine  \hfill 2017
 %   \item Nonlinear Dynamical Systems | ODEs \hfill 2017
 %   \item Computational Modeling and Simulation of Biol. Systems  \hfill 2017
 %   \item Machine Learning for Bioinformatics  \hfill 2017
 %   \item  Neural Systems \& Anatomy \hfill 2017
 %   \item Dynamics of Neural Microcircuits \hfill 2017
 %   \item Neuroengineering  \hfill 2016
    % UWM
 %   \item \textbf{UWM}
 %   \item Probability Models \hfill 2016
 %   \item Linear Algebra + Differential Equations \hfill 2015
 %   \item Neuropharmacology \hfill 2015
 %   \item Neuroscience \hfill 2015
 %   \item Physiological Psychology \hfill 2014
 %   \item Neuropsychology \hfill 2013
    
%\end{cvlist}

\end{document}  